### 2023-06-26 README.Rmd
updated version 230626

<li><code>kl</code>: Kullback-Leibler-Divergence which measures the
divergence between the actual choice distribution and the predicted
choice distribution (Ding et al., 2011; Drost, 2018). Output provides both
divergence between predicted from observed and observed from predicted
due to the asymmetry of the Kullback-Leibler divergence. If you specify
an optional <code>Group</code> argument the output is split by
groups.</li>

@@

In the next step, we would like to see how well our model (from which we took the raw utilities) predict the choices in the validation/ holdout task. First, we will test the <code>hitrate()</code> function. We specify the <code>data</code>, the column index of <code>id</code>, the column index of the alternatives (<code>opts</code>; remember we have three alternatives + the *no-buy* alternative), and finally the column index of the choice. We can see that the hitrate of our example is `r round(hitrate(data = HOT, id = 1, opts = c(2:5), choice = 6)[3, 1], digits  = 3)`.

>>>>

<li><code>kl</code>: Kullback-Leibler-Divergence which measures the
divergence between the actual choice distribution and the predicted
choice distribution (Ding et al., 2011; Drost, 2018). Output provides both
divergence between predicted from observed and observed from predicted
due to the asymmetry of the Kullback-Leibler divergence. If you specify
an optional <code>Group</code> argument the output is split by
groups. Currently, you can choose between \eqn{log{_2}} and \eqn{log} as logarithm base.</li>

@@

In the next step, we would like to see how well our model (from which we took the raw utilities) predict the choices in the validation/ holdout task. First, we will test the <code>hitrate()</code> function. We specify the <code>data</code>, the column index of <code>id</code>, the column index of the alternatives (<code>opts</code>; remember we have three alternatives + the *no-buy* alternative), and finally the column index of the choice. We can see that the hitrate of our example is `r round(as.numeric(hitrate(data = HOT, id = 1, opts = c(2:5), choice = 6)[3, 2]), digits  = 3)`.
